### 2018-06-04 ms-thesis-slides.tex
initial commit

%!TEX program = xelatex
\documentclass[aspectratio=169]{beamer}

\usepackage{blindtext}

\usetheme{AVThesis}

\title{The Art of Robotics:\\A Holistic Approach}
\subtitle{Master of Science in Robotics\\Thesis Defense}
\author{Alexander Volkov Jr.}
\date{August 5, 2018}

\setcounter{showSlideNumbers}{1}

\begin{document}
	\setcounter{showProgressBar}{0}
	\setcounter{showSlideNumbers}{0}

	\frame{\titlepage}

	\begin{frame}
		\frametitle{Contents}
		\begin{enumerate}
			\item Introduction \\ \textcolor{AVThesisGrey}{\footnotesize\hspace{1em} The reasoning and background behind this theme}
			\item Lorem Text  \\ \textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Just some Lorem Ipsum for filler}
			\item Conclusions \\ \textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Some closing thoughts}
		\end{enumerate}
	\end{frame}

	\setcounter{framenumber}{0}
	\setcounter{showProgressBar}{1}
	\setcounter{showSlideNumbers}{1}
	\section{Introduction}
		\begin{frame}
			\frametitle{Why Beamer?}
			\begin{enumerate}
				\item LaTeX is great!
				\item Beamer is easy to use!
				\item Why not?
			\end{enumerate}
		\end{frame}

		\begin{frame}
			\frametitle{Why Custom Themes?}
			\begin{itemize}
				\item The default Beamer themes are outdated and visually displeasing
				\item There aren't many Beamer themes readily available online
				\item Making custom Beamer themes is easy!
			\end{itemize}
		\end{frame}

	\section{Lorem Ipsum}
		\begin{frame}
			\frametitle{Lorem 1}
			\blindtext
		\end{frame}

		\begin{frame}
			\frametitle{Lorem 2}
			\blindtext
		\end{frame}

		\begin{frame}
			\frametitle{Lorem 3}
			\blindtext
		\end{frame}

	\section{Conclusions}
		\begin{frame}
			\frametitle{Closing Thoughts}
			\begin{itemize}
				\item Woo, Beamer!
			\end{itemize}
		\end{frame}

	\appendix
	\backupbegin
	  \begin{frame}
	    \frametitle{Backup slide 1}
	    \blindtext
	  \end{frame}
	\backupend

\end{document}

### 2018-07-26 ms-thesis-slides.tex
working on slides, writing up abstract for announcement

@@
 
-\title{The Art of Robotics:\\A Holistic Approach}
+\title{The Art of Robotics:\\\vspace{0.2em}\huge{Towards A Holistic Approach}}
 \subtitle{Master of Science in Robotics\\Thesis Defense}
 \author{Alexander Volkov Jr.}
-\date{August 5, 2018}
+\date{July 31, 2018}
+
+% Change frame margins
+\addtobeamertemplate{frametitle}{\vspace*{1cm}}{\vspace*{0cm}}
 
@@
 	\begin{frame}
-		\frametitle{Contents}
+		\frametitle{Talk Agenda}
 		\begin{enumerate}
-			\item Introduction \\ \textcolor{AVThesisGrey}{\footnotesize\hspace{1em} The reasoning and background behind this theme}
-			\item Lorem Text  \\ \textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Just some Lorem Ipsum for filler}
-			\item Conclusions \\ \textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Some closing thoughts}
+			\item Other Things \\ 
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Warm up the crowd with a quick review of some other things I've done.}
+			\item The Big Picture \\ 
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Cover the central themes of this talk.}
+
+			\item Bond Graphs, Impedance/Admittance Matching \\
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} An old framework, revived.}
+
+			\item Brushless PMSM Motors \\
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Operating limits, thermal management, liquid cooling.}
+
+			\item Touching Robots \\
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, whiskers, robot pain.}
+
+			\item Conclusions \\ 
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Review key points and propose some future work.}
+
+			\item Questions \\
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} \emph{``Please clap...''}}
 		\end{enumerate}
@@
 	\setcounter{showSlideNumbers}{1}
-	\section{Introduction}
+
+	\section{Other Things}
 		\begin{frame}
-			\frametitle{Why Beamer?}
+			\frametitle{Teaching}
+			Gelfand Center
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Tangential Projects}
+			Kruskal count + quadruped gaits
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Robotics Institute Meme Facebook Page}
+			Started the RI's first and only meme page
+			Current stats?
+			Some meme examples?
+		\end{frame}
+
+	\section{The Big Picture}
+		\begin{frame}
+			\frametitle{}
 			\begin{enumerate}
@@
 			\end{enumerate}
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{Why Custom Themes?}
-			\begin{itemize}
-				\item The default Beamer themes are outdated and visually displeasing
-				\item There aren't many Beamer themes readily available online
-				\item Making custom Beamer themes is easy!
-			\end{itemize}
 		\end{frame}
@@
 
+	\section{Questions?}
+
 	\appendix

### 2018-07-29 ms-thesis-slides.tex
moving stuff around, switched to Lualatex build
adding slides, ri memes stuff

@@
-%!TEX program = xelatex
+%!TEX program = lualatex
 \documentclass[aspectratio=169]{beamer}
@@
 \usepackage{blindtext}
+\usepackage{multimedia}
 
@@
 
-\title{The Art of Robotics:\\\vspace{0.2em}\huge{Towards A Holistic Approach}}
+\title{The Art of Robotics:\\\vspace{0.2em}\huge{Toward A Holistic Approach}}
 \subtitle{Master of Science in Robotics\\Thesis Defense}
@@
 		\begin{enumerate}
-			\item Other Things \\ 
+			\setlength{\itemsep}{4mm}
+			\item Background
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} How I ended up here.}
+
+			\item Other Things
 				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Warm up the crowd with a quick review of some other things I've done.}
-			\item The Big Picture \\ 
+
+			\item The Big Picture
 				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Cover the central themes of this talk.}
 
-			\item Bond Graphs, Impedance/Admittance Matching \\
+			\item A Unifying Framework
 				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} An old framework, revived.}
 
-			\item Brushless PMSM Motors \\
+			\item Brushless PMSM Motors
 				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Operating limits, thermal management, liquid cooling.}
 
-			\item Touching Robots \\
-				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, whiskers, robot pain.}
+			\item Touching Robots
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, contact modeling, whiskers, robot pain.}
 
-			\item Conclusions \\ 
+			\item Conclusions
 				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Review key points and propose some future work.}
 
-			\item Questions \\
+			\item Questions
 				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} \emph{``Please clap...''}}
@@
 
+	\section{Background}
+		\begin{frame}
+			\frametitle{How I Ended Up Here}
+
+		\end{frame}
+
 	\section{Other Things}
 		\begin{frame}
-			\frametitle{Teaching}
-			Gelfand Center
+			\frametitle{Teaching with CMU's Gelfand Outreach Center}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=center] (gelfand-logo) at (0.88\textwidth, 0) {\includegraphics[width=5cm]{media/gelfand-logo.jpg}};
+			\end{tikzpicture}
+			\begin{itemize}
+				\item Introduction to Robotics with the Finch Platform
+					\begin{itemize}
+						\item Each session is 5 days, 3 hrs/day
+						\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
+						\item 1 session Summer 2017 + 2 sessions Summer 2018
+					\end{itemize}
+					\vspace{1em}
+
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Teaching with CMU's Gelfand Outreach Center}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=center] (gelfand-logo) at (0.88\textwidth, 0) {\includegraphics[width=5cm]{media/gelfand-logo.jpg}};
+			\end{tikzpicture}
+			\begin{itemize}
+				\item Saturday Series LEGO WeDo Robotics
+				\begin{itemize}
+					\item 3 hour course
+					\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
+					\item 1 session Spring 2018
+				\end{itemize}
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Robotics Institute Meme Facebook Page}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Robotics Institute Meme Facebook Page}
+			\begin{itemize}
+				\item Some statistics:
+					\begin{itemize}
+						\item The RI's first and only meme page
+						\item Formed in March 2018
+						\item 170 members
+						\item 30 memes, 23 original contributions!
+					\end{itemize}
+			\end{itemize}
+	\end{frame}
+
+	\section{The Big Picture}
+		\begin{frame}
+			\frametitle{Breadth First}
+			\begin{enumerate}
+				\item 
+			\end{enumerate}
 		\end{frame}
@@
 
+	\section{A Unifying Framework}
 		\begin{frame}
-			\frametitle{Robotics Institute Meme Facebook Page}
-			Started the RI's first and only meme page
-			Current stats?
-			Some meme examples?
-		\end{frame}
-
-	\section{The Big Picture}
-		\begin{frame}
-			\frametitle{}
-			\begin{enumerate}
-				\item LaTeX is great!
-				\item Beamer is easy to use!
-				\item Why not?
-			\end{enumerate}
-		\end{frame}
-
-	\section{Lorem Ipsum}
-		\begin{frame}
-			\frametitle{Lorem 1}
-			\blindtext
+			\frametitle{The Port-Hamiltonian Framework}
+			\begin{itemize}
+				\item Port-based Analysis
+				\item Hamiltonian Dynamics
+					\begin{itemize}
+						\item 
+					\end{itemize}
+				\item
+			\end{itemize}
 		\end{frame}
@@
 		\begin{frame}
-			\frametitle{Lorem 2}
-			\blindtext
+			\frametitle{Bond Graphs}
+
 		\end{frame}
@@
 		\begin{frame}
-			\frametitle{Lorem 3}
-			\blindtext
+			\frametitle{Hamiltonian Dynamics}
+
 		\end{frame}
 
-	\section{Conclusions}
+		\begin{frame}
+			\frametitle{Putting it All Together}
+
+		\end{frame}
+
+	\section{Brushless PMSM Motors}
+
+		\begin{frame}
+			\frametitle{???}
+		\end{frame}
+
+	\section{Touching Robots}
+
+		\begin{frame}
+			\frametitle{The Most Important Sensory Modality}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Contact Models}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Terminator 2 Got It Right}
+			\begin{center}
+			\movie[height = 0.6\textwidth, width = 0.8\textwidth,showcontrols]{}{media/terminator2-pain.mp4}
+			\end{center}
+		\end{frame}
+
+	\section{Closing Thoughts}
 		\begin{frame}

### 2018-07-31 ms-thesis-slides.tex
wow, such progress, much work

@@
 \documentclass[aspectratio=169]{beamer}
+% add 'handout' to beamer options for printout
 
-\usepackage{blindtext}
 \usepackage{multimedia}
+\usepackage[backend=biber,style=ieee]{biblatex}
 
@@
 
-\title{The Art of Robotics:\\\vspace{0.2em}\huge{Toward A Holistic Approach}}
+\title{The Art of Robotics:\\\vspace{0.2em}\huge{Toward a Holistic Approach}}
 \subtitle{Master of Science in Robotics\\Thesis Defense}
@@
 \date{July 31, 2018}
+
+\bibliography{refs/thesis-slides.bib}
 
@@
 			\item Background
-				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} How I ended up here.}
+				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} The BFD; how I ended up here}
 
-			\item Other Things
-				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Warm up the crowd with a quick review of some other things I've done.}
+%			\item Other Things
+%				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Warm up the crowd with a quick review of some other things I've done.}
 
@@
 
-			\item Brushless PMSM Motors
-				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Operating limits, thermal management, liquid cooling.}
+%			\item Brushless PMSM Motors
+%				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Operating limits, thermal management, liquid cooling.}
 
@@
 
-			\item Questions
+			\item Acknowledgments \& Questions
 				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} \emph{``Please clap...''}}
@@
 	\section{Background}
-		\begin{frame}
-			\frametitle{How I Ended Up Here}
-
-		\end{frame}
-
-	\section{Other Things}
-		\begin{frame}
-			\frametitle{Teaching with CMU's Gelfand Outreach Center}
-			\begin{tikzpicture}[overlay, remember picture]
-				\node[anchor=center] (gelfand-logo) at (0.88\textwidth, 0) {\includegraphics[width=5cm]{media/gelfand-logo.jpg}};
-			\end{tikzpicture}
-			\begin{itemize}
-				\item Introduction to Robotics with the Finch Platform
-					\begin{itemize}
-						\item Each session is 5 days, 3 hrs/day
-						\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
-						\item 1 session Summer 2017 + 2 sessions Summer 2018
-					\end{itemize}
-					\vspace{1em}
-
-			\end{itemize}
-		\end{frame}
 
 		\begin{frame}
-			\frametitle{Teaching with CMU's Gelfand Outreach Center}
-			\begin{tikzpicture}[overlay, remember picture]
-				\node[anchor=center] (gelfand-logo) at (0.88\textwidth, 0) {\includegraphics[width=5cm]{media/gelfand-logo.jpg}};
-			\end{tikzpicture}
+			\frametitle{The BFD}
 			\begin{itemize}
-				\item Saturday Series LEGO WeDo Robotics
+				\item \textbf{End Game:} Develop a Unified Framework for Understanding Robotics \pause
 				\begin{itemize}
-					\item 3 hour course
-					\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
-					\item 1 session Spring 2018
+					\item \textbf{Thesis Purpose:} Reflect on and organize \emph{my} understanding of robotics \pause
+						\begin{itemize}
+							\item \textbf{Talk Purpose:} Provide an overview of my thesis dissertation for the committee
+						\end{itemize}
 				\end{itemize}
@@
 		\begin{frame}
-			\frametitle{Robotics Institute Meme Facebook Page}
+			\frametitle{Talk Title Etymology I}
 			\begin{tikzpicture}[overlay, remember picture]
-				\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
+				\node[anchor=east] (taoe) at ($(current page.east)+(-3mm,-1mm)$) 	{\includegraphics[width=5.5cm]{media/the-art-of-electronics.png}};
+			\end{tikzpicture}
+			\begin{itemize}
+				\item ``The Art of Electronics'', by \emph{Horowitz \& Hill}\pause
+				\begin{itemize}
+					\item Literally the electrical engineering bible
+					\item Incredibly thorough
+					\item Perfect balance of practicality and rigor 
+				\end{itemize}
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Talk Title Etymology II}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=east] (taoe) at ($(current page.east)+(-10mm,-1mm)$) 	{\includegraphics[width=4cm]{media/mason-manip-book.jpg}};
+			\end{tikzpicture}
+			\begin{itemize}
+				\item ``Mechanics of Robotic Manipulation'', by \emph{Mason}\footnotemark~\autocite{mason2001mechanics} \pause
+					\begin{itemize}
+						\item ``Manipulation is an art\dots'' (p.1)
+					\end{itemize}
+			\end{itemize}
+			\footnotetext{Matt, I'll take my referral payments by mail.}
+		\end{frame}
+
+%		\begin{frame}
+%			\frametitle{Talk (Sub)Title Etymology III}
+%			\begin{tikzpicture}[overlay, remember picture]
+%			\fontsize{18}{15}
+%			\node[anchor=center] (subtitle) at (current page.center) {``Toward a Holistic Approach''};
+%			\end{tikzpicture}
+%		\end{frame}
+%		
+%		\begin{frame}
+%			\addtocounter{framenumber}{-1}
+%			\frametitle{Talk (Sub)Title Etymology III}
+%			\begin{tikzpicture}[overlay, remember picture]
+%				\fontsize{18}{15}
+%				\node[anchor=center] (subtitle) at (current page.center) {``\highlight{toward}{Toward} a Holistic Approach''};
+%				\fontsize{10}{12}
+%				\node[anchor=south west, fill=red!20,rounded corners, text width=3cm, outer sep=3pt, inner sep=3pt] (toward-note) at ($(current page.south west) + (10mm,10mm)$) {When you concede falling short of a goal in academia.};
+%				\draw [->, line width=0.3mm] (toward-note) -- (toward);
+%			\end{tikzpicture}
+%		\end{frame}
+
+		\begin{frame}
+%			\addtocounter{framenumber}{-1}
+			\frametitle{Talk (Sub)Title Etymology III}
+			\begin{tikzpicture}[overlay, remember picture]
+				\fontsize{18}{15}
+				\only<1>{\node[anchor=center] (subtitle) at (current page.center) {``Toward a Holistic Approach''};}
+				\only<2>{\node[anchor=center] (subtitle) at (current page.center) {``\highlight{toward}{Toward} a Holistic Approach''};
+				\fontsize{10}{12}
+				\node[anchor=south west, fill=red!20,rounded corners, text width=5cm, outer sep=3pt, inner sep=3pt] (toward-note) at ($(current page.south west) + (10mm,10mm)$) {When you concede falling short of a goal in academia.
+Example: Mason's Annual Review ``Toward Robotic Manipulation'' \autocite{Mason2018}};
+				\draw [->, line width=0.3mm] (toward-note) -- (toward);}
+				\onslide<3->{\node[anchor=center] (subtitle) at (current page.center) {``\highlight{toward}{Toward} a \highlight{holistic}{Holistic} Approach''};
+				\fontsize{10}{12}
+				\node[anchor=south west, fill=red!20,rounded corners, text width=5cm, outer sep=3pt, inner sep=3pt] (toward-note) at ($(current page.south west) + (10mm,10mm)$) {When you concede falling short of a goal in academia.
+Example: Mason's Annual Review ``Toward Robotic Manipulation'' \autocite{Mason2018}};
+				\draw [->, line width=0.3mm] (toward-note) -- (toward);
+				\node[anchor=south east, fill=red!20,rounded corners, text width=7cm, outer sep=3pt, inner sep=3pt] (holistic-note) at ($(current page.south east) + (-10mm,10mm)$) {From the mechatronics/systems engineering community.
+Chhabra and Emami provide an excellent summary in \autocite{Chhabra2011}.};
+				\draw [->, line width=0.3mm] (holistic-note) -- (holistic);}
 			\end{tikzpicture}
@@
 		\begin{frame}
-			\frametitle{Robotics Institute Meme Facebook Page}
+			\frametitle{How I Ended Up Here (Some Context) I}
+			\vspace{-0.5em}
 			\begin{itemize}
-				\item Some statistics:
+				\item \textbf{Hobby robotics} $\Rightarrow$ self-taught basic electronics, programming, CAD\pause
 					\begin{itemize}
-						\item The RI's first and only meme page
-						\item Formed in March 2018
-						\item 170 members
-						\item 30 memes, 23 original contributions!
+						\item ``Keep it cheap''
+						\item ``Keep it open-source''
+						\item ``Keep it useful (or, at least, artistic)''
+					\end{itemize}\pause
+				\vspace{0.5em}
+				\item \textbf{Cornell Undergrad} $\Rightarrow$ ECE major, ME/CS minors\pause
+					\begin{itemize}
+						\item \textbf{ECE:}
+							\begin{itemize}
+								\item ``Everything is an impedance (or an admittance)''
+								\item ``What's the system bandwidth?''
+							\end{itemize}
+						\item \textbf{ME:}\pause
+							\begin{itemize}
+								\item ``At the end of the day, everything is mechanical''
+								\item ``Everything is a model, and every model is wrong''
+							\end{itemize}\pause
+						\item \textbf{CS:} 
+						\begin{itemize}
+							\item ``90\% of solving a problem is finding the right representation''
+							\item ``Everything breaks at the interfaces''
+						\end{itemize}
 					\end{itemize}
@@
 
-	\section{The Big Picture}
 		\begin{frame}
-			\frametitle{Breadth First}
-			\begin{enumerate}
-				\item 
-			\end{enumerate}
+			\frametitle{How I Ended Up Here (Some Context) II}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=center] (ri-logo) at (current page.center) {\includegraphics[width=30mm]{assets/ri-logo.eps}};
+				\node[minimum width=2cm, below=5mm of ri-logo] {``Time to become a robotics master...''};
+			\end{tikzpicture}
 		\end{frame}
@@
 		\begin{frame}
-				\frametitle{Tangential Projects}
-				Kruskal count + quadruped gaits
+			\frametitle{How I Ended Up Here (Some Context) III}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{10}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {``Legged locomotion is cool...''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) IV}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{10}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {\color{gray}``Legged locomotion is cool...''};
+				\node[anchor=north east] (hartmut) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/hartmut.jpg}};
+				\node[anchor=north east] (travers) at ($(current page.north east)+(-28mm,-15mm)$) {\includegraphics[width=2cm]{media/travers.jpg}};
+				\node[anchor=north east] (koushil) at ($(current page.north east)+(-51mm,-15mm)$) {\includegraphics[width=2cm]{media/koushil.jpg}};
+				\node[anchor=east, minimum width=2cm, left=3mm of koushil] {``Great! Here's absolutely no funding.''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) V}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{10}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {``Umm...''};
+				\node[anchor=north east] (hartmut) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/hartmut.jpg}};
+				\node[anchor=north east] (travers) at ($(current page.north east)+(-28mm,-15mm)$) {\includegraphics[width=2cm]{media/travers.jpg}};
+				\node[anchor=north east] (koushil) at ($(current page.north east)+(-51mm,-15mm)$) {\includegraphics[width=2cm]{media/koushil.jpg}};
+				\node[anchor=east, minimum width=2cm, left=3mm of koushil] {\color{gray}``Great! Here's absolutely no funding.''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) VI}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{10}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {\color{gray}``Umm...''};
+				\node[anchor=north east] (ross) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/ross.jpg}};
+				\node[anchor=east, minimum width=2cm, left=3mm of ross] {``Wait! Go talk to Matt Mason!''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) VII}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{10}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {``(skeptical) Okay...''};
+				\node[anchor=north east] (ross) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/ross.jpg}};
+				\node[anchor=east, minimum width=2cm, left=3mm of ross] {\color{gray}``Wait! Go talk to Matt Mason!''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) VIII}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{15}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {\color{gray}``(skeptical) Okay...''};
+				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
+				\node[anchor=east, text width=5cm, left=3mm of matt, align=right] {``Manipulation is awesome! \\And I have money! \\And I don't micromanage!''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) IX}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{15}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {``(excited) Works for me!''};
+				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
+				\node[anchor=east, text width=5cm, left=3mm of matt, align=right] {\color{gray}``Manipulation is awesome! \\And I have money! \\And I don't micromanage!''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) X}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{15}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[minimum width=2cm, right=3mm of me] {\color{gray}``(excited) Works for me!''};
+				\node[anchor=north east] (matt) at ($(current page.north east)+(-5mm,-15mm)$) {\includegraphics[width=2cm]{media/mason.jpg}};
+				\node[anchor=east, minimum width=2cm, left=3mm of matt, align=right] {``Fantastic, go forth and prosper!''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) XI}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=south east] (ri-logo) at ($(current page.south east)+(-5mm,10mm)$) {\includegraphics[width=16mm]{assets/ri-logo.eps}};
+				\fontsize{12}{15}
+				\node[anchor=south west] (me) at ($(current page.south west)+(5mm,10mm)$) {\includegraphics[width=2cm]{media/me.jpg}};
+				\node[text width=8cm, right=3mm of me, align=left] {``I've been meaning to read Hogan's famous \emph{Impedance Control}~\autocite{hogan1985impedance} paper, I guess I'll start there...''};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{How I Ended Up Here (Some Context) XII}
+			\begin{tikzpicture}[overlay, remember picture]
+				\fontsize{18}{15}
+				\node[anchor=center, minimum width=2cm] at (current page.center) {\dots~Two Years Later \dots};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+		\frametitle{Me, circa July 2018}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=center] (paranoid) at (current page.center) {\includegraphics[width=8cm]{media/charlie-paranoid}};
+				\node[anchor=center, below=0mm of paranoid] {``So it's all about causality\dots~and feedback!''};
+			\end{tikzpicture}
+		\end{frame}
+
+	\section{The Big Picture}
+		\begin{frame}
+			\frametitle{Back to Basics}
+			\begin{itemize}[<+->]
+				\item Want a concise \emph{theory of robotics}\dots
+				\item Interested in the \emph{physics} common to robotics problems
+				\item Not worried about SLAM, POMDPs, etc\dots~there are bigger fish to fry (we're skimming over the basics!)
+					\begin{itemize}
+						\item i.e. Moravec's paradox \autocite{moravec1988mind}
+					\end{itemize}
+				\item Inherently a \emph{breadth-first} approach, since we're looking for a unifying framework
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Problem 1: What is a Robot?}
+			\begin{itemize}
+				\item I know it's a cliché to bring this up\dots \pause but I must! \pause
+				\begin{itemize}
+					\item Does the ambiguity really matter? \pause
+					\item Maybe not, but some unifying \emph{theme} would be useful!
+				\end{itemize}
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Problem 2: Locomotion and Manipulation, Segregated}
+			\begin{itemize}
+				\item Locomotion and manipulation are studied separately in robotics\pause
+					\begin{itemize}
+						\item \dots~and biomechanics, for that matter
+						\item Seems quite natural at first, we all talk about the two as separate specializations in robotics
+					\end{itemize}\pause
+				\item Eventually, the notion of \emph{``duality''} comes up\dots
+				\begin{itemize}\pause
+					\item Locomotion and manipulation sometimes overlap
+						\begin{itemize}
+							\item Pai et al.'s \emph{Platonic Beasts} \autocite{pai1994platonic}
+							\item Mason et al.'s \emph{Mobipulator} \autocite{MasonMobileManipulator1999} \autocite{MasonDesktopMobileManipulators2000}
+							\item Also, literally everywhere in biology
+						\end{itemize}
+					\item Perhaps it just comes down to a change of reference?
+						\begin{itemize}
+							\item What pushes off of what?
+							\item Locomotion is ``self-manipulation'', e.g. Aaron Johnson's PhD thesis \autocite{johnson2014self} and related works \autocite{johnson2012standing}\autocite{johnson2016hybrid}
+						\end{itemize}
+				\end{itemize}
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Problem 2: Locomotion and Manipulation, United}
+			\begin{itemize}
+				\item Taking the ``self-manipulation'' perspective
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Embodiment \& Hogan's Physical-Equivalence Principle}
+			\begin{itemize}[<+->]
+				\item Embodiment
+					\begin{itemize}
+						\item 
+						\item Presently resides in the cognitive science community (as in ``embodied \emph{cognition}'')
+					\end{itemize}
+				\item 
+			\end{itemize}
 		\end{frame}
@@
 		\begin{frame}
+			\frametitle{Dissipative Elements}
+		\end{frame}
+
+		\begin{frame}
 			\frametitle{Putting it All Together}
@@
 
-	\section{Brushless PMSM Motors}
+	\section{Touching Robots}
 
 		\begin{frame}
-			\frametitle{???}
+			\frametitle{A Note on Stiffness and Collisions}
+			\begin{itemize}
+				\item \textbf{\color{red}STOP COLLIDING STIFF OBJECTS AND EXPECTING RELIABLE RESULTS}
+			\end{itemize}
 		\end{frame}
-
-	\section{Touching Robots}
 
@@
 
-	\section{Questions?}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\setcounter{showProgressBar}{0}
+	\setcounter{showSlideNumbers}{0}
 
@@
 	\backupbegin
+
+	\section{Acknowledgments}
+
 	\begin{frame}
-	    \frametitle{Backup slide 1}
-	    \blindtext
+	\frametitle{Cheers}
+		Committee\\Lab\\The other profs\\Jean\\Cameron\\Cats\\Parents for debt free education
 	\end{frame}
+
+	\section{Questions?}
+
+	\nocite{*}
+	\begin{frame}[allowframebreaks]
+		\frametitle{Bibliography}
+		\printbibliography[heading=none]
+	\end{frame}
+
+		\section{Other Things}
+	\begin{frame}
+	\frametitle{Teaching with CMU's Gelfand Outreach Center}
+	\begin{tikzpicture}[overlay, remember picture]
+	\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
+	\end{tikzpicture}
+	\vspace{9em}
+	\begin{itemize}
+		\item Introduction to Robotics with the Finch Platform
+		\begin{itemize}
+			\item Each session is 5 days, 3 hrs/day
+			\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
+			\item 1 session Summer 2017 + 2 sessions Summer 2018
+		\end{itemize}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Teaching with CMU's Gelfand Outreach Center}
+\begin{tikzpicture}[overlay, remember picture]
+\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
+\end{tikzpicture}
+\vspace{9em}
+\begin{itemize}
+\item Saturday Series LEGO WeDo Robotics
+\begin{itemize}
+	\item 3 hour course
+	\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
+	\item 1 session Spring 2018
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Robotics Institute Meme Facebook Page}
+\begin{tikzpicture}[overlay, remember picture]
+\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
+\end{tikzpicture}
+\end{frame}
+
+\begin{frame}
+\frametitle{Robotics Institute Meme Facebook Page}
+\vspace{9em}
+\begin{itemize}
+\item Some statistics:
+\begin{itemize}
+\item The RI's first and only meme page
+\item Formed in March 2018
+\item 170 members
+\item 30 memes, 23 original contributions!
+\end{itemize}
+\end{itemize}
+\begin{tikzpicture}[overlay, remember picture]
+\node[anchor=south east] (ri-meme-3) at ($(current page.south east) + (2mm,5mm)$) {\includegraphics[width=7.5cm]{media/ri-meme-manifold-optimization.jpg}};
+\end{tikzpicture}
+\begin{tikzpicture}[overlay, remember picture]
+\node[anchor=north east] (ri-meme-1) at ($(current page.north east) + (-45mm,-12mm)$) {\includegraphics[width=3.5cm]{media/ri-meme-thesis-anxiety.jpg}};
+\end{tikzpicture}
+\begin{tikzpicture}[overlay, remember picture]
+\node[anchor=north west] (ri-meme-2) at ($(current page.north west) + (10mm,-12mm)$) {\includegraphics[width=5cm]{media/ri-meme-ros-sleep.jpg}};
+\end{tikzpicture}
+\end{frame}
+
 	\backupend

### 2018-07-31 ms-thesis-slides.tex
almost there...

@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) II}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) III}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) IV}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) V}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) VI}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) VII}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) VIII}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) IX}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) X}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) XI}
@@
 		\begin{frame}
+			\addtocounter{framenumber}{-1}
 			\frametitle{How I Ended Up Here (Some Context) XII}
@@
 		\begin{frame}
-
+			\frametitle{Problem 2: What is Manipulation?}
+			\begin{itemize}
+				\item To be honest, I had a very shallow understanding of manipulation until I met Matt \pause
+					\begin{itemize}
+						\item I imagined it was just factory robot stuff \pause
+						\item It took some reflection to appreciate the depth of ``manipulation''
+					\end{itemize}
+			\end{itemize}
 		\end{frame}
@@
 		\begin{frame}
-			\frametitle{Problem 2: Locomotion and Manipulation, Segregated}
+			\frametitle{Problem 2: What is Manipulation?}
+			\begin{tikzpicture}[overlay, remember picture]
+				\fontsize{15}{12}
+				\node[anchor=center, text width=0.8\textwidth,align=center] (manip-def) at ($(current page.center)+(0,-3mm)$) {``Manipulation refers to an agent’s control of its environment through selective contact.''};
+				\small
+				\node[anchor=south east, align=right] at ($(current page.south east)+(-1cm,1cm)$) {--- \emph{Matt Mason}, ``Toward Robotic Manipulation'' \autocite{Mason2018}};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Problem 3: Locomotion and Manipulation, Segregated}
 			\begin{itemize}
@@
 						\begin{itemize}
-							\item What pushes off of what?
+							\item Just a matter of ``what pushes off of what?''
 							\item Locomotion is ``self-manipulation'', e.g. Aaron Johnson's PhD thesis \autocite{johnson2014self} and related works \autocite{johnson2012standing}\autocite{johnson2016hybrid}
@@
 		\begin{frame}
-			\frametitle{Problem 2: Locomotion and Manipulation, United}
+			\frametitle{Problem 3: Locomotion and Manipulation, United}
+			\vspace{-6em}
 			\begin{itemize}
-				\item Taking the ``self-manipulation'' perspective
+				\item The ``self-manipulation'' view of locomotion is consistent with our definition of ``manipulation'':
+					\begin{itemize}
+						\item An agent may control its environment through selective contact (i.e. ``manipulation'') by moving about in it (i.e. ``locomotion''). \footnotemark
 					\end{itemize}
+			\end{itemize}
+			\footnotetext{It helps to take on an egocentric point of view to visualize this.}
+			\pause
+			\begin{tikzpicture}[overlay, remember picture]
+				\fontsize{15}{12}
+				\node[anchor=center,text width=0.8\textwidth,align=center] (loco-manip) at ($(current page.center)+(0,-10mm)$) {So locomotion is just a subset of manipulation!};
+			\end{tikzpicture}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Problem 3: Locomotion and Manipulation, United}
+			\begin{itemize}
+				\item Not a terribly practical insight\dots \pause~but thinking back to \emph{Problem 1}\dots
+			\end{itemize}
+			\begin{tikzpicture}[overlay, remember picture]
+				\node[anchor=center,text width=0.8\textwidth,align=center] (loco-manip) at ($(current page.center)+(0,-10mm)$) {So locomotion is just a subset of manipulation!};
+			\end{tikzpicture}
 		\end{frame}
@@
 		\begin{frame}
-			\frametitle{The Port-Hamiltonian Framework}
+			\frametitle{Port-Hamiltonian Systems Theory}
 			\begin{itemize}
 				\item Port-based Analysis
+					\begin{itemize}
+						\item Inherits the bond-graph notion of power ports
+						\item Treats systems in terms of power flow between components
+						\item Each bond represents the conjugate pair of an effort and flow
+					\end{itemize}\pause
 				\item Hamiltonian Dynamics
 					\begin{itemize}
-						\item 
+						\item Provides a fully geometric (intrinsic, coordinate free) description of system dynamics
+						\item Equivalent to (and convertible from/to) Lagrangian formulation
+							\begin{itemize}
+								\item Whereas Lagrangian dynamics derives solely from variation principles, the Hamiltonian formulation 
+								\item Riemannian geometry of Lagrangian dynamics replaced with symplectic geometry, in which fundamental invariants are preserved.
+								\item Configuration space of Lagrangian dynamics replaced with state space
 							\end{itemize}
-				\item
+					\end{itemize}
 			\end{itemize}
@@
 		\begin{frame}
-			\frametitle{Bond Graphs}
+			\frametitle{Bond-Graphs}
 
@@
 
+	\section{Bibliography}
 	\nocite{*}

### 2018-08-02 ms-thesis-slides.tex
talk done!

@@
 %!TEX program = lualatex
-\documentclass[aspectratio=169]{beamer}
+\documentclass[aspectratio=169,handout]{beamer}
 % add 'handout' to beamer options for printout
@@
 
-			\item Touching Robots
-				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, contact modeling, whiskers, robot pain.}
-
+%			\item Touching Robots
+%				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, contact modeling, whiskers, robot pain.}
+%			
 			\item Conclusions
@@
 			\begin{itemize}
-				\item I know it's a cliché to bring this up\dots \pause but I must! \pause
+				\item I know it's a cliché to bring this up\dots \pause~but I must! \pause
 				\begin{itemize}
@@
 			\begin{tikzpicture}[overlay, remember picture]
-				\node[anchor=center,text width=0.8\textwidth,align=center] (loco-manip) at ($(current page.center)+(0,-10mm)$) {So locomotion is just a subset of manipulation!};
+				\node[anchor=center,text width=0.8\textwidth,align=center] (manip-is-king) at ($(current page.center)+(0,-10mm)$) {\Large \color{red} Manipulation \emph{is} the central theme in robotics!};
 			\end{tikzpicture}
@@
 		\begin{frame}
-			\frametitle{Embodiment \& Hogan's Physical-Equivalence Principle}
+			\frametitle{Embodiment \& Hogan's Physical-Equivalence ``Postulate''}
 			\begin{itemize}[<+->]
@@
 					\begin{itemize}
-						\item 
+						\item Vaguely, the idea that robots exist in the real world and are inherently tied to their environment
 						\item Presently resides in the cognitive science community (as in ``embodied \emph{cognition}'')
 					\end{itemize}
-				\item 
+				\item \emph{Hogan's} Physical-Equivalent Principle
+					\begin{itemize}
+						\item ``It is impossible tO devise a controller which will cause a physical system to present an apparent behavior 10 its environment which is distinguishable from that of a purely physical system'' \autocite{hogan1985impedance}
+						\item Basic argument for this is ``you can't break thermodynamic laws''
+						\item But more intuitively, the robot is a real thing, you can't make it do not real things
+					\end{itemize}
 			\end{itemize}
@@
 	\section{A Unifying Framework}
+		\begin{frame}
+			\frametitle{Port-Hamiltonian Systems Theory}
+			\begin{itemize}[<+->]
+				\item The symbiosis of:
+					\begin{itemize}[<+->]
+						\item Bond graph theory (\emph{Paynter, Hogan, Breedveld, van Dijk})
+						\item Hamiltonian dynamics on manifolds (i.e. ``geometric mechanics'')
+						\item Poisson / Dirac structures
+					\end{itemize}
+				\item Principal contributors include \emph{Stramigioli, van der Schaft, Maschke}
+			\end{itemize}
+		\end{frame}
+
 		\begin{frame}
@@
 						\item Each bond represents the conjugate pair of an effort and flow
-					\end{itemize}\pause
+					\end{itemize}
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Port-Hamiltonian Systems Theory}
+			\begin{itemize}
 				\item Hamiltonian Dynamics
@@
 						\item Provides a fully geometric (intrinsic, coordinate free) description of system dynamics
-						\item Equivalent to (and convertible from/to) Lagrangian formulation
+						\item Equivalent to (and convertible from/to) Lagrangian formulation, but better!
 							\begin{itemize} 
-								\item Whereas Lagrangian dynamics derives solely from variation principles, the Hamiltonian formulation 
-								\item Riemannian geometry of Lagrangian dynamics replaced with symplectic geometry, in which fundamental invariants are preserved.
+								\item Riemannian geometry of Lagrangian dynamics replaced with symplectic geometry, in which fundamental invariants are preserved
 								\item Configuration space of Lagrangian dynamics replaced with state space
+								\item Hamiltonian formulation directly yields a system of first order differential equations
+							\end{itemize}
+						\item Avoiding nonholonomic constraints yields explicit ODE\footnote{May be a stiff explicit ODE! So, soften your intermittent contacts!}
+					\end{itemize}
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}
+			\frametitle{Port-Hamiltonian Systems Theory}
+			\begin{itemize}
+				\item System fully defined by: 
+					\begin{itemize}
+						\item Energy function captures all energy storage elements in system
+						\item Resistive structure captures all dissipative elements in system
+						\item Poisson or Dirac interconnection structure defines power flow within system
+							\begin{itemize}
+								\item \emph{Storage port} connects to energy storage
+								\item \emph{Dissipative port} connects to resistive structure
+								\item \emph{Interaction port} connects to environment (\textbf{dynamic system} not known a-priori or directly controlled)
+								\item \emph{Controller port} connects to controller (\textbf{dynamic system} that the designer has control over)
 							\end{itemize}
@@
 		\begin{frame}
-			\frametitle{Bond-Graphs}
-
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{Hamiltonian Dynamics}
-
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{Dissipative Elements}
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{Putting it All Together}
-
-		\end{frame}
-
-	\section{Touching Robots}
-
-		\begin{frame}
-			\frametitle{A Note on Stiffness and Collisions}
-			\begin{itemize}
-				\item \textbf{\color{red}STOP COLLIDING STIFF OBJECTS AND EXPECTING RELIABLE RESULTS}
-			\end{itemize}
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{The Most Important Sensory Modality}
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{Contact Models}
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{Terminator 2 Got It Right}
-			\begin{center}
-			\movie[height = 0.6\textwidth, width = 0.8\textwidth,showcontrols]{}{media/terminator2-pain.mp4}
-			\end{center}
+			\frametitle{Working Through an Example}
 		\end{frame}
@@
 			\begin{itemize}
-				\item Woo, Beamer!
+				\item Manipulation is the common theme in robotics
+				\item Embodiment \Leftrightarrow Hogan's Physical Equivalence Principle \autocite{hogan1985impedance}
+				\item Port-Hamiltonian Systems Theory is the framework to unify robotics
 			\end{itemize}
@@
 
+%		\begin{frame}
+%	\frametitle{Teaching with CMU's Gelfand Outreach Center}
+%	\begin{tikzpicture}[overlay, remember picture]
+%	\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
+%	\end{tikzpicture}
+%	\vspace{9em}
+%	\begin{itemize}
+%		\item Introduction to Robotics with the Finch Platform
+%		\begin{itemize}
+%			\item Each session is 5 days, 3 hrs/day
+%			\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
+%			\item 1 session Summer 2017 + 2 sessions Summer 2018
+%		\end{itemize}
+%	\end{itemize}
+%\end{frame}
+%
+%\begin{frame}
+%\frametitle{Teaching with CMU's Gelfand Outreach Center}
+%\begin{tikzpicture}[overlay, remember picture]
+%\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
+%\end{tikzpicture}
+%\vspace{9em}
+%\begin{itemize}
+%\item Saturday Series LEGO WeDo Robotics
+%\begin{itemize}
+%	\item 3 hour course
+%	\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
+%	\item 1 session Spring 2018
+%\end{itemize}
+%\end{itemize}
+%\end{frame}
+%
+%\begin{frame}
+%\frametitle{Robotics Institute Meme Facebook Page}
+%\begin{tikzpicture}[overlay, remember picture]
+%\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
+%\end{tikzpicture}
+%\end{frame}
+%
+%\begin{frame}
+%\frametitle{Robotics Institute Meme Facebook Page}
+%\vspace{9em}
+%\begin{itemize}
+%\item Some statistics:
+%\begin{itemize}
+%\item The RI's first and only meme page
+%\item Formed in March 2018
+%\item 170 members
+%\item 30 memes, 23 original contributions!
+%\end{itemize}
+%\end{itemize}
+%\begin{tikzpicture}[overlay, remember picture]
+%\node[anchor=south east] (ri-meme-3) at ($(current page.south east) + (2mm,5mm)$) {\includegraphics[width=7.5cm]{media/ri-meme-manifold-optimization.jpg}};
+%\end{tikzpicture}
+%\begin{tikzpicture}[overlay, remember picture]
+%\node[anchor=north east] (ri-meme-1) at ($(current page.north east) + (-45mm,-12mm)$) {\includegraphics[width=3.5cm]{media/ri-meme-thesis-anxiety.jpg}};
+%\end{tikzpicture}
+%\begin{tikzpicture}[overlay, remember picture]
+%\node[anchor=north west] (ri-meme-2) at ($(current page.north west) + (10mm,-12mm)$) {\includegraphics[width=5cm]{media/ri-meme-ros-sleep.jpg}};
+%\end{tikzpicture}
+%\end{frame}
+
 	\begin{frame}
 	\frametitle{Cheers}
-		Committee\\Lab\\The other profs\\Jean\\Cameron\\Cats\\Parents for debt free education
+		\begin{itemize}
+			\item Matt Mason
+			\item Aaron Johnson \& Will Martin
+			\item The MLab
+			\item Ross Knepper, Hod Lipson, Ephrahim Garcia, Boris Kogan, Mike Meller
+			\item Jean Harpley
+			\item Cameron
+			\item Malcolm X, Nina Simone, and George Harrison
+			\item Parents
+		\end{itemize}
 	\end{frame}
@@
 
-	\section{Other Things}
-	\begin{frame}
-	\frametitle{Teaching with CMU's Gelfand Outreach Center}
-	\begin{tikzpicture}[overlay, remember picture]
-	\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
-	\end{tikzpicture}
-	\vspace{9em}
-	\begin{itemize}
-		\item Introduction to Robotics with the Finch Platform
-		\begin{itemize}
-			\item Each session is 5 days, 3 hrs/day
-			\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
-			\item 1 session Summer 2017 + 2 sessions Summer 2018
-		\end{itemize}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Teaching with CMU's Gelfand Outreach Center}
-\begin{tikzpicture}[overlay, remember picture]
-\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
-\end{tikzpicture}
-\vspace{9em}
-\begin{itemize}
-\item Saturday Series LEGO WeDo Robotics
-\begin{itemize}
-	\item 3 hour course
-	\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
-	\item 1 session Spring 2018
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Robotics Institute Meme Facebook Page}
-\begin{tikzpicture}[overlay, remember picture]
-\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
-\end{tikzpicture}
-\end{frame}
-
-\begin{frame}
-\frametitle{Robotics Institute Meme Facebook Page}
-\vspace{9em}
-\begin{itemize}
-\item Some statistics:
-\begin{itemize}
-\item The RI's first and only meme page
-\item Formed in March 2018
-\item 170 members
-\item 30 memes, 23 original contributions!
-\end{itemize}
-\end{itemize}
-\begin{tikzpicture}[overlay, remember picture]
-\node[anchor=south east] (ri-meme-3) at ($(current page.south east) + (2mm,5mm)$) {\includegraphics[width=7.5cm]{media/ri-meme-manifold-optimization.jpg}};
-\end{tikzpicture}
-\begin{tikzpicture}[overlay, remember picture]
-\node[anchor=north east] (ri-meme-1) at ($(current page.north east) + (-45mm,-12mm)$) {\includegraphics[width=3.5cm]{media/ri-meme-thesis-anxiety.jpg}};
-\end{tikzpicture}
-\begin{tikzpicture}[overlay, remember picture]
-\node[anchor=north west] (ri-meme-2) at ($(current page.north west) + (10mm,-12mm)$) {\includegraphics[width=5cm]{media/ri-meme-ros-sleep.jpg}};
-\end{tikzpicture}
-\end{frame}
-
 	\backupend
